Secure Composition of Robust and Optimising Compilers

### 2023-07-09 popl/main.tex
sec3 sketch examples

@@

@@

>>>>

\begin{example}[A program satisfying \gls{tms}]
  Consider the following program which, when run, yields the trace $\ev{Alloc}\ \loc[_{1}]\ 17;\comp;\unlock\cdot\ev{Use}\ \loc[_{1}]\ 5;\comp;\unlock\cdot\ev{Use}\ \loc[_{1}]\ 5;\comp;\unlock\cdot\ev{Dealloc}\ \loc[_{1}];\comp;\unlock$, where $\loc[_{1}]$ is some memory address determined by the semantics of the programming language.
  \begin{lstlisting}[language=c,basicstyle=\ttfamily,morekeywords={new,delete}]
int main() {  // allocates 17 integers initialized to 2
  int* x = new[17](2);

  x[5] = 12;
  int y = x[5];
  delete x;

  return y;
}
  \end{lstlisting}
  Relating the trace to abstract monitor events yields $\abstrace=\absev{Alloc}\ \loc[_{1}]\ \comp\cdot\absev{Use}\ \loc[_{1}]\ \comp\cdot\absev{Use}\ \loc[_{1}]\ \comp\cdot\absev{Dealloc}\ \loc[_{1}]\ \comp$.
  It is easy to see that $\montmssafe{\abstrace}$.
  From \Thmref{lem:mon:tmsafe}, it follows that the program satisfies \Thmref{def:trace:tmsdef}.
\end{example}

@@

\begin{example}[\texttt{strncpy}]\label{ex:strncpy:sms}
  Consider the \texttt{strncpy} functions from \Cref{ex:strncpy}.
  \MKin{do trace and explain why monitor finds out that it violates sms prop}
\end{example}

@@

\begin{example}[DIT on vs DIT off]
  \MKin{fill in the blank}
\end{example}
